Our best attempt at fixing the internet

### 2013-12-22 paper.tex
Removing PDFs

\section{Scope}
This paper attempts to fix the confidentiality features of the Internet by introducing a distributed and non-hierarchical domain name system and providing a replacement for TCP at the transport layer.. Meta-data, that can be connected at the IP-level such as the source and destination of a communications will still be collectable. Nevertheless, we think that the suggested enhancements of this paper should help anonymity projects like The Tor Project to speed up substantially their network which is one of their key issues. (Tor project investigates SPEEDY)

\section{Motivation}
When the Internet was designed at DARPA, the primary goal was to design a system that could provide interconnection between multiple computers. The Web then came by with the motivation to be able to freely exchange information. The Internet has mainly been used for open communications. Any computer on the network could request files. But, over time, people started trusting the internet more and more and with the appearance of services. But the Internet grew so quickly out of what DARPA proposed for a trusted environment. The threat model of the internet changed and our

>>>>

\subsection{Scope}
This paper attempts to fix the confidentiality features of the Internet by introducing a distributed and non-hierarchical domain name system and providing a replacement for TCP at the transport layer.. Meta-data, that can be connected at the IP-level such as the source and destination of a communications will still be collectable. Nevertheless, we think that the suggested enhancements of this paper should help anonymity projects like The Tor Project to speed up substantially their network which is one of their key issues. (Tor project investigates SPEEDY)

\subsection{Motivation}
When the Internet was designed at DARPA, the primary goal was to design a system that could provide interconnection between multiple computers. The Web then came by with the motivation to be able to freely exchange information. The Internet has mainly been used for open communications. Any computer on the network could request files. But, over time, people started trusting the internet more and more and with the appearance of services. But the Internet grew so quickly out of what DARPA proposed for a trusted environment. The threat model of the internet changed and our
